---
title: "PicoGreen protocol for 1 plate of samples, standards" 
subtitle: "xxxx xx xx"
output: pdf_document
fontsize: 12 pt
header-includes:
  \pagenumbering{gobble}
  \usepackage{longtable}
  \usepackage{caption}
---

\captionsetup[table]{labelformat=empty}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(kableExtra)
```

- standards made up in triplicate
- calibration plate with triplicate standards
- 96-well sample plate

Preparation

- label 1x TE, PicoGreen (PG) centrifuge tubes
- label optical plates. Gen5 protocols are set for Costar 96 black opaque 3915
- have on hand 1 full box each of P10, P200 tips + 4 columns P200
- turn on plate reader in advance of use

1. prepare 1x TE buffer (10 mM Tris-HCl, 1 mM EDTA, ph 7.5) from the supplied 20x

purpose |               -        |  expansion | - | with overage
- | - | - | - | -
96 samples         | @ 99 ul ea  |  9 500
120 vol. dilute PG | @ 100 ul ea | 12 000     | @ 1.09 | 13 100
standards          | separate protocol  |  3 930
__total__              |      -      | 25 430 | @ 1.09 | __27 700__

-  26 315 ul H2O
-   1 385  ul 20X TE

2. aliquot off 13 034.5 ul 1x TE for PG solution
3. drop 99 ul of 1x TE in the sample plate wells

\pagebreak

4. drop in 100 ul standard curve per well on calibration plate

$\cdot$ | 1 | 2 | 3
- | - | - | -
A | 1x TE | 1x TE | 1x TE
B | 64  | 64  | 64 ng / ml
C | 128 | 128 | 128
D | 256 | 256 | 256
E | 512 | 512 | 512
F | 640 | 640 | 640
G | 800 | 800 | 800
H | 1000 | 1000 |1000

5. homogenize dna on thermomixer 1 min. 400 rpm, 4C. 
6. drop tips for negative controls, both boxes
7. spin down microplate
8. add 1 ul to each sample well

```{r}
miss <- tibble(` ` = LETTERS[1:8], `1` = rep(" ", 8), '2' = rep (" ", ),
               `3` = rep(" ", 8), `4` = rep(" ", 8), `5` = rep(" ", 8), 
               `6` = rep(" ", 8), `7` = rep(" ", 8), `8` = rep(" ", 8),
               `9` = rep(" ", 8), `10` = rep(" ", 8), `11` = rep(" ", 8), `12` = rep(" ", 8))
kbl(miss, caption = "missed aliquots: catch with a P10", longtable = TRUE) %>% kable_styling()
```

9. prepare a 200-fold dilution of PG in 1x TE

- Keep reagent in foil while thawing and in diluted state. Vortex well, spin down.
- For 13 100 ul pg solution:  
    - 13 034.5 ul 1x TE
    - 65.5 ul PG

10. Add 100 ul diluted PG to every well. Aspirate 10X. New tips each time, both plates.
11. Cover optical plates with old Costar plates or foil. Incubate at RT for 5 min.
12. Read the plates.



