\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{tmargin=0.75in, bmargin=0.75in, lmargin=1.5in, rmargin=0.75in}

\title{QIAamp DNA Micro Kit 56304 extraction \\ from dried fin clip punches}
\author{sample description}
\date{xxxx xx xx}

\begin{document}

\maketitle

\section*{Points before starting}
\begin{itemize}
    \item centrifugation done at room temperature. place columns in centrifuge in a consistent position so that fluid takes the same path each time
    \item reconstituted RNA not to exceed 3 freeze/thaw cycles
    \item thermomixer holds 24 tubes. set up lysis for all 24 at end of day. carry out bind/wash/elute the next morning in 3 rounds of 8 samples each
    \item protocol goes through 5 collection tubes per sample. ethanol (96-100\%) is required
\end{itemize}

\section*{Things to do before starting}
\begin{itemize}
    \item Before using Buffers AW1 and AW2 for the first time, add the appropriate amount of ethanol (96-100\%) to obtain working solutions
    \item Buffers ATL and AL may form precipitates upon storage. Warm at 56C with gentle agitation until dissolved. Can both check for precipitates by pouring off into beakers and pipette from same
    \item reconstitute lypholized RNA in 310 ul AE. aliquot into 0.5 ml tubes, store -20C
    \item set up single-level program on thermomixer for infinite time, 56C, and 1200 rpm for incubation
        \subitem set interval mix option to 30 s mixing time, 30 min. pause
\end{itemize}

\section*{Lysing with ATL:proteinase K}
\begin{enumerate}
    \item load dried fin clip punches into labelled 1.7 ml Safe-lock centrifuge tubes
    \item add 180 ul ATL to each of all 24 centrifuge tubes
    \item load ethanol-stored samples
    \item add 20 ul pro-K to each tube in turn and pulse-vortex 6X
    \item check that punches are submerged and lids are tight
    \item incubate samples overnight on thermomixer 

\end{enumerate}

\pagebreak

\section*{Binding with AL, ethanol}
prep:label tubes, spin columns as you go
\begin{enumerate}
    \item centrifuge 3 min. at > 1200 x g, transfer lysate without debris to new 1.7 ml tube
    \item make MM of 200 ul buffer AL and 1 ul RNA per. pulse-vortex 6X
    \item NH dried fin clips only: add AL/RNA to each tube, pulse-vortex 6X
    \item add AL only to IPOR samples, pulse-vortex 6X
    \item add 200 ul chilled ethanol to each tube, cap, pulse-vortex each in turn 6X
    \item incubate 5 min. at RT, spin down
    \item transfer lysate to spin column in collection tube without wetting the rim
    \begin{itemize}
        \item NH samples get micro spin columns, IPOR samples standard
        \item avoid transferring foam from lysis or touching upper column area. apply sample only to membrane. close cap gently and move tubes carefully to avoid splashing
    \end{itemize}
    \item centrifuge 3 min at 1200 rpm
    \item centrifuge 1 min at 8000 rpm (6000 x g). ensure lysate has cleared spin column
\end{enumerate}

\section*{First wash with AW1}
\begin{enumerate}
    \item place spin column in a new 2 ml collection tube, discarding flow-through and collection tube
    \item add 500 ul AW1  
    \item centrifuge for 1 min at 8000 rpm
\end{enumerate}

\section*{Second wash with AW2}
\begin{enumerate}
    \item place spin column in a new 2 ml collection tube, discarding flow-through and collection tube
    \item add 500 ul AW2
    \item centrifuge 1 min at 14,000 rpm (20,000 g)
    \item remove spin column from the collection tube, avoiding column contact with flow-through
    \item place spin column in new collection tube, discarding flowthrough and collection tube
    \item centrifuge 3 min at 14,000 rpm (20,000 g)
    \begin{center}
    \emph{increased centrifugation dries the membrane, avoiding ethanol contamination}
    \end{center}
\end{enumerate}

\section*{Elution with AE}
\begin{enumerate}
    \item place spin column in a new, labelled 1.7 ml microcentrifuge tube (not provided)
    \item pipette 100 ul Buffer AE directly onto membrane
    \item incubate 5 min. at room temp
    \item centrifuge for 1 min at 14,000 rpm
    \item aliquot 30 ul as working stock. store -80C, -20C respectively
\end{enumerate}

\end{document}
